---
title: "Lab02 - t tests and confidence intervals for ANOVA"
author: "Your Name Here"
output: pdf_document
---

## Goals

The goal in this lab is to get some practice working with t-based inference for ANOVA models in R.

## Loading packages

Here are some packages with functionality you may need for this lab.  Run this code chunk now.

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(mosaic)
library(gmodels)

options("pillar.sigfig" = 10) # print 10 significant digits in summarize output
```

## Reading in the Spock data

The following R code reads in the data set for the Spock Trial and takes a first look at the data.  Run this code now; no need to modify it.

```{r}
juries <- read_csv("http://www.evanlray.com/data/sleuth3/ex0502_women_jurors.csv")

dim(juries)
head(juries)

juries %>% count(Judge)
```

## Make some plots

Use this space to make some plots of the Spock trial data.

```{r}
ggplot(data = juries, mapping = aes(x = Judge, y = Percent)) +
  geom_boxplot()
```

```{r}
ggplot(data = juries, mapping = aes(x = Percent)) +
  geom_histogram() +
  facet_wrap( ~ Judge)
```

## t tests and confidence intervals

Use this space to conduct hypothesis tests and find confidence intervals.

```{r}
fit <- lm(Percent ~ Judge, data = juries)
```

#### Below is code relevant to part 2 (a) on the handout from 2019-02-04

```{r}
library(gmodels)
fit.contrast(fit, "Judge", c(1, 0, 0, 0, 0, 0, -1), conf.int = 0.95)
```


```{r}
juries %>%
  group_by(Judge) %>%
  summarize(
    mean_pct_women = mean(Percent)
  )
```

```{r}
34.12 - 14.62
```



#### Below is code relevant to part 2 (b) on the handout from 2019-02-04

```{r}
library(gmodels)
fit.contrast(fit, "Judge", c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6, -1), conf.int = 0.95)
```

The formatting of the output above is not good.  Below I'm dropping that extra junk to make the results easier to read.

```{r}
temp <- fit.contrast(fit, "Judge", c(1/6, 1/6, 1/6, 1/6, 1/6, 1/6, -1), conf.int = 0.95)
rownames(temp) <- NULL
temp
```
